### 2023-08-18 paper/sec-dis-pseudodata.tex
faserv fiducial length

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the beginning of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$ 
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 30~{\rm cm}$ {\color{blue} [MF: Is 30 cm correct? The length I have is 100 cm. Looking at \cite{FASER:2023zcr}, I think that the final length of tungsten might be closer to 80cm = 730 layers * 1.1mm/layer]}.
%
The FASER apparatus is immersed in a magnetic field  providing charged lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.

>>>>

\paragraph{FASER$\nu$.}
%
The ForwArd Search ExpeRiment (FASER) detector
and its companion FASER$\nu$~\cite{FASER:2019aik,FASER:2019dxq,FASER:2023zcr,FASER:2022hcn}
are located at the TI12 tunnel of the CERN accelerator complex.
%
Both detectors are aligned
with the collision axis line-of-sight (LOS)
and have been acquiring data since the beginning of Run III in 2022.
%
Neutrino scattering takes place in the FASER$\nu$ 
detector, composed by interleaved emulsion and tungsten plates and
adding up to a mass of 1.1 tons with a fiducial volume of $20~\rm{cm} \times 25~\rm{cm} \times 80~{\rm cm}$.
%
The FASER apparatus is immersed in a magnetic field  providing charged lepton
identification thanks to two 1 m-long dipole magnets with $B=0.57$ T
and another 1.5 m-long magnet in front of the spectrometer. 
%
Neutrino detection and identification can be carried out either using the emulsion
films of FASER$\nu$2, which have the key benefit of excellent position and angular resolution,
or instead using the electronic detector components of FASER, which enable the tagging
of the outgoing downstream energetic muons.
%
FASER$\nu$ is sensitive to neutrinos with pseudorapidity $\eta_\nu \ge 8.5$
and can also identify charm-tagged events.
